---
title: "duanResourcesDb"
author: "Amanda Zacharias"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Computational Genomics Lab Resources for Students

A database used to keep track of various resources that are used by the Computational Genomics / Duan Laboratory. Currently limited to an html with searchable datasets.
To contribute to the database, users must interact with the github repository (instructions to be added). 


```{r echo=FALSE}
# Dependencies
library(DBI) # 1.1.3
library(RSQLite) # 2.2.20
library(DT) # 0.30
```

```{r echo=FALSE}
# Load SQLite database
resourcesDb <- dbConnect(RSQLite::SQLite(), dbname = "./duanResourcesDb.sqlite")
```


## Resources {.tabset}
### Tools
```{r echo=FALSE}
toolsDf <- dbGetQuery(resourcesDb, "SELECT * FROM tools")
datatable(data = toolsDf, 
          options = list(
            autoWidth = TRUE
            )
          )
```

### Datasets
```{r echo=FALSE}
toolsDf <- dbGetQuery(resourcesDb, "SELECT * FROM databases")
datatable(data = toolsDf, 
          options = list(
            autoWidth = TRUE
            )
          )
```

### Papers
```{r echo=FALSE}
toolsDf <- dbGetQuery(resourcesDb, "SELECT * FROM papers")
datatable(data = toolsDf, 
          options = list(
            autoWidth = TRUE
            )
          )
```

## How to contribute: 
Be capable of using github and RSQLite


```{r echo = FALSE}
# End SQLite connection
dbDisconnect(resourcesDb)
```

